---
title: "How to Create a PDF in Quarto"
author: "Qingyin Cai"
date: today
format:
  pdf:
    documentclass: article
    fontsize: 12pt
    geometry: margin=1in
    toc: false
    number-sections: true
    fig-cap-location: top
execute:
  echo: true
  warning: false
  message: false
---

# Overview

This documentation shows you how to generate a **PDF** from a Quarto (`.qmd`) document.

::: callout-note
**What you’ll learn**    

1. Install the LaTeX engine (TinyTeX).  

2. Write a minimal `.qmd` file.  

3. Render to PDF from RStudio/VS Code/Terminal.  

4. Troubleshoot common errors.
:::

# Prerequisites

- **Quarto** installed: <https://quarto.org/docs/get-started/>
- A LaTeX engine. The easiest is **TinyTeX** (lightweight TeX Live).  
  - If you use R, run in R/RStudio:

```r
install.packages("tinytex")
tinytex::install_tinytex()
```

- Alternatively install **TeX Live** (Linux/macOS) or **MiKTeX** (Windows).

# Minimal Example

Create a file named `mydoc.qmd` with the content below:

```markdown
---
title: "My First PDF in Quarto"
author: "Student Name"
format: pdf
---

# Introduction

This is my first PDF created with **Quarto**!
```

## Render the PDF

**Option A: RStudio / VS Code**
- Open `mydoc.qmd` and click **Render**.

**Option B: Terminal**
```bash
quarto render mydoc.qmd
```

The output file will be `mydoc.pdf` in the same folder.

# Customizing the PDF

You can customize the PDF via YAML:

```yaml
---
title: "Research Report"
author: "Student Name"
date: today
format:
  pdf:
    documentclass: article
    fontsize: 12pt
    geometry: margin=1in
    toc: true
    number-sections: true
---
```

## Sections, Equations, Figures, and Tables

### Math
Inline math like $y = \beta_0 + \beta_1 x + \varepsilon$, and a display equation:

$$
\hat{\beta} = (X'X)^{-1}X'y.
$$

### Figure

```{r}
#| label: fig-scatter
#| fig-cap: "Example scatter plot"
#| echo: false
set.seed(1)
x <- rnorm(100)
y <- 0.5 * x + rnorm(100, sd = 0.5)
plot(x, y, pch = 19, xlab = "x", ylab = "y")
```

### Table

```{r}
#| label: tab-summary
#| tbl-cap: "Summary statistics"
#| echo: false
summary(data.frame(x = x, y = y))
```


# Troubleshooting

**Problem:** *"LaTeX Error: File `xyz.sty` not found"*  
**Fix:** Install the missing package. If using TinyTeX in R:

```r
tinytex::tlmgr_install("xyz")
```

**Problem:** *Quarto can’t find LaTeX*  
**Fix:** Ensure TinyTeX/MiKTeX/TeX Live is installed and on your PATH; restart RStudio/VS Code.
